---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CIMPLE

<!-- badges: start -->
<!-- badges: end -->

The goal of CIMPLE is to offer a collection of methods involved with analyzing longitudinal EHR data with possibly informative observational time. These methods are grouped into two classes depending on the inferential task. One group focuses on estimating the effect of an exposure on a longitudinal biomarker while the other group assesses the impact of a longitudinal biomarker on time-to-diagnosis outcomes. 

## Installation

You can install the development version of CIMPLE from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jiacongD/CIMPLE")
```

## Example

A very basic workflow:

```{r example}
library(CIMPLE)

time_var = "time"
id_var = "id"
outcome_var = "Y"
VPM_variables = c("Z", "X")
LM_fixedEffect_variables = c("Z", "X")
LM_randomEffect_variables = "Z"

# Run the standard LME model
fit_standardLME = long_est(
  long_data = train_data,
  method = "standard_LME",
  id_var = id_var,
  outcome_var = outcome_var,
  LM_fixedEffect_variables = LM_fixedEffect_variables,
  time = time_var,
  LM_randomEffect_variables = LM_randomEffect_variables,
  VPM_variables = VPM_variables
)

# Return the coefficient estimates
fit_standardLME$beta_hat
```
